Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
resize graphs and finalize paper

```{r fig.pos="H"}
#| echo: false
#| message: false
#| label: tbl-gender-strip-search
#| tbl-cap: Summary Statistics of Gender Identities against Police Strip Searches

@@

```{r fig.height=3, fig.width=5}
#| echo: false
#| message: false
#| label: fig-gender-strip-search
#| fig-cap: Gender Identities and Police Strip Search Per Arrest in Toronto, 2020-2021

@@

```{r fig.width=7, fig.height=2.5, fig.pos="H"}
#| echo: false
#| warning: false
#| message: false
#| label: fig-reasons-race
#| fig-cap: Relationship Between Reasons for Strip Search and Race in Toronto, 2020-2021
#| layout-ncol: 1
#| fig-subcap: ["Black and White","Other Minority Groups and White"]

@@

```{r fig.height=3 , fig.width=8}
#| echo: false
#| message: false
#| warning: false
#| label: fig-reasons-gender
#| fig-cap: Relationship Between Reasons for Strip Search and Gender in Toronto, 2020-2021

>>>>

```{r}
#| echo: false
#| message: false
#| label: tbl-gender-strip-search
#| tbl-cap: Summary Statistics of Gender Identities against Police Strip Searches

@@

```{r fig.height=4, fig.width=5}
#| echo: false
#| message: false
#| label: fig-gender-strip-search
#| fig-cap: Gender Identities and Police Strip Search Per Arrest in Toronto, 2020-2021

@@

```{r fig.width=7.5, fig.height=4, fig.pos="H"}
#| echo: false
#| warning: false
#| message: false
#| label: fig-reasons-race
#| fig-cap: Relationship Between Reasons for Strip Search and Race in Toronto, 2020-2021
#| layout-ncol: 1
#| fig-subcap: ["Black and White","Other Minority Groups and White"]

@@

```{r fig.height=4.5 , fig.width=8}
#| echo: false
#| message: false
#| warning: false
#| label: fig-reasons-gender
#| fig-cap: Relationship Between Reasons for Strip Search and Gender in Toronto, 2020-2021
